Model based reinforcement learning at FERMI FEL

### 2020-11-16 main.tex
txs auto checkin

\section{Uncertainty aware Dyna-style reinforcement learning}
The original Dyna algorithm \cite{DYNA} is modified here in several aspects. Generally, Dyna style algorithms denote algorithms, where a MFRL algorithm is trained on purely synthetic data from an approximate dynamics model or on a mixture of synthetic and real data. We use only synthetic data to reduce the interaction with the real environment to a minimum.
An overview of the used method is shown in \cref{fig:MBRL_overview}. At the beginning the data is collected or read in from a pre-collection. An uncertainty aware model is trained, using anchored ensembles on the data, which allows to take the allegorical (measurement errors) as well as the epistemic uncertainty (lack of data) into account. Subsequently a MFRL algorithm is deployed to learn the controller on the learned model by only using the synthetic data, by taking the uncertainty into account. After a defined number of training steps the controller is testes on each model individually. If there is no improvement in a specific ratio$<1$ of models, the controller is tested on the real environment.

\begin{figure}[!h]
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/MBRL_overview}
	\caption{A schematic overview of the AE-Dyna approach used in this paper.}
	\label{fig:MBRL_overview}
\end{figure}
\subsection{What was tested?}
\begin{itemize}
	\item The ANN - including the prior - number of models
	\item The number of data points and the policy
	\item The uncertainty - how is this included
	\item The episodic design
	\item ...
\end{itemize}
\subsection{Operational deployment}
\NB{Niky} % come abbiamo interagito con FERMI
\subsection{\NB{short FERMI introduction}}
The Free Electron laser Radiation for Multidisciplinary Investigation  better known as the FERMI, is the seeded free-electron laser facility next to the third-generation synchrotron facility ELETTRA at the Elettra Sinchrotrone Trieste laboratories.
A free-electron laser is a fourth-generation light source where the lasing medium consists of very-high-speed electron moving freely through a magnetic structure. The FERMI peculiarity is given by the usage of an external seeding source that provides several advantages, as the increased stability in pulse and photon energy, reduced size of the device, improved longitudinal coherence, more control on the pulse structure, and improved temporal synchronization with external timing systems.

>>>>

\section{Uncertainty aware Dyna-style reinforcement learning}
The original Dyna algorithm \cite{DYNA} is modified here in several aspects. Generally, Dyna style algorithms denote algorithms, where a MFRL algorithm is trained on purely synthetic data from an approximate dynamics model or on a mixture of synthetic and real data. We use only synthetic data to reduce the interaction with the real environment to a minimum.
An overview of the used method is shown in \cref{fig:MBRL_overview}. At the beginning the data is collected or read in from a pre-collection. An uncertainty aware model is trained, using anchored ensembles on the data, which allows to take the allegorical (measurement errors) as well as the epistemic uncertainty (lack of data) into account. Subsequently a MFRL algorithm is deployed to learn the controller on the learned model by only using the synthetic data, by taking the uncertainty into account. After a defined number of training steps the controller is testes on each model individually. If there is no improvement in a specific ratio$<1$ of models, the controller is tested on the real environment for a number of episodes. The training is stopped if the controller solves the problem on the real environement.

\begin{figure}[!h]
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/MBRL_overview}
	\caption{A schematic overview of the AE-Dyna approach used in this paper.}
	\label{fig:MBRL_overview}
\end{figure}
\subsection{What was tested?}
\begin{itemize}
	\item The ANN - including the prior - number of models - noise level
	\item The number of data points and the policy
	\item The uncertainty - how is this included
	\item The episodic design
	\item ...
\end{itemize}
\subsection{Operational deployment}
\NB{Niky} % come abbiamo interagito con FERMI
\subsection{\NB{short FERMI introduction}}
The Free Electron laser Radiation for Multidisciplinary Investigation  better known as the FERMI, is the seeded free-electron laser facility next to the third-generation synchrotron facility ELETTRA at the Elettra Sinchrotrone Trieste laboratories.
A free-electron laser is a fourth-generation light source where the lasing medium consists of very-high-speed electron moving freely through a magnetic structure. The FERMI peculiarity is given by the usage of an external seeding source that provides several advantages, as the increased stability in pulse and photon energy, reduced size of the device, improved longitudinal coherence, more control on the pulse structure, and improved temporal synchronization with external timing systems.
